Title

### 2018-08-24 thesis/paper/paper.tex
Inequalities with longer letter predicates paper

An entity \(e \in E\) is always a string and can be written as \(c_0 \ldots c_{l - 1}\) with \(l = len(e)\) being the length of the string. Denote the set \(C = \{c | \exists e \in E: c \in e\}\)\todo{\(c \in e\) does not seem correct} as the set of characters occurring in entities. Then \(l_{\max} = \max\limits_{\forall e \in E}(len(e))\) is the length of the longest entity string. Based on this a group of predicates letter\_iEDB[2] is introduced where \(i \in \{0 \ldots l_{\max}-1\}\) and letter\_iEBD denotes the ith letter of the entity string.\\

For each entity string \(e = c_0 \ldots c_{l - 1}\) each predicate letter\_iEDB is created as \(\text{letter\_iEDB}(e, f(e, i))\), where
\begin{equation*}
f(e, i) = 
\begin{cases}
      c_i & i < len(e) \\
      \text{NONE} & i \geq len(e)
\end{cases}
\end{equation*}

Now that inequality between all constitution characters and the link between entities and their characters are introduced, the inequality between two entities can be derived by creating the following rules for all predicates letter\_i:
\begin{equation*}
\text{unequal}(X, Y) \leftarrow \text{letter\_i}(X, A) \wedge \text{letter\_i}(Y, B) \wedge \text{unequal}(A, B)
\end{equation*}

>>>>

An entity \(e \in E\) is always a string and can be written as \(c_0 \ldots c_{l - 1}\) with \(l = len(e)\) being the length of the string. Denote the set \(C = \{c | \exists e \in E: c \in e\}\)\todo{\(c \in e\) does not seem correct} as the set of characters occurring in entities. Then \(l_{\max} = \max\limits_{\forall e \in E}(len(e))\) is the length of the longest entity string.
Based on this a group of predicates letter\_i\_EDB[8] is introduced where \(0 \equiv i \mod 7\), \(0 \leq i < l_{max} \).

For each entity string \(e = c_0 \ldots c_{l - 1}\) each predicate letter\_i\_EDB is created as \(\text{letter\_i\_EDB}(e, f(e, i), f(e, i+1), \ldots, f(e, i+6)\), where
\begin{equation*}
f(e, i) = 
\begin{cases}
      c_i & i < len(e) \\
      \text{NONE} & i \geq len(e)
\end{cases}
\end{equation*}

Now that inequality between all constitution characters and the link between entities and their characters are introduced, the inequality between two entities can be derived by creating the following rules for all predicates letter\_i (with \text{letters} short for \(\text{letter\_i}(X, A_i, \ldots, A_{i+14}) \wedge\text{letter\_i}(Y, B_i, \ldots, B_{i+6})\)):
\begin{equation*}
\text{unequal}(X, Y) \leftarrow \text{letters} \wedge \text{unequal}(A_i, B_i)
\end{equation*}
\begin{equation*}
\text{unequal}(X, Y) \leftarrow \text{letters} \wedge \text{unequal}(A_{i+6}, B_{i+6})
\end{equation*}
